Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-03 cav2017/cav2017.tex
wording
spacing

We consider models of physical plants expressed as ordinary differential
equations (ODEs), which we assume to be controllable and under full state
information (i.e., we have access to all the model variables):
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
\end{align}
%
where $t \in \mathbb R_0^+$, where $A$ and $B$ are matrices that fully
specify the continuous plant, and with initial states set as $x(0)$.  While
we ideally would like to work on the continuous-time plant, in this work
Eq.~\eqref{eq:ode} is soundly discretized in time~\cite{fadali} into
%
%\textcolor{red}{What is subscript ``d''?}
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k
\end{align} 
%
where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state.  $A_d$ and
$B_d$ denote the matrices that describe the discretized plant dynamics, whereas
$A$ and $B$ denote the continuous plant dynamics.  Later, we will address the
issue of variable quantization, as introduced by the ADC/DAC conversion
blocks (Fig.~\ref{fig:digitalsystem}).

@@

We illustrate our approach with an example,
extracted from the literature~\cite{Franklin15}.
%
We start with a candidate solution with all coefficients zero, $K=[0
  \ 0 \ 0]^T$, and a precision of $I_p=13$, $F_p=3$.  In the first
{\sc verify} stage, the {\sc safety} check finds the counterexample
%
$ x_0 = [-0.5 \ 0.5 \ 0.5] $.
%
After adding the new counterexample to its sets of {\sc inputs}, {\sc
  synthesize} finds the candidate solution $K=[0 \ 0
  \ 0.00048828125]^T$, which prompts the {\sc safety} verifier to
return $x_0=[-0.5 -0.5 -0.5]$ as the new counterexample.

>>>>

We consider models of physical plants expressed as ordinary differential
equations (ODEs), which we assume to be controllable and under full state
information (i.e., we have access to all the model variables):
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
\end{align}
%
where $t \in \mathbb R_0^+$, where $A$ and $B$ are matrices that fully
specify the continuous plant, and with initial states set as $x(0)$.  While
ideally we would like to work on the continuous-time plant, in this work
Eq.~\eqref{eq:ode} is soundly discretized in time~\cite{fadali} into
%
%\textcolor{red}{What is subscript ``d''?}
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k
\end{align} 
%
where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state.  $A_d$ and
$B_d$ denote the matrices that describe the discretized plant dynamics, whereas
$A$ and $B$ denote the continuous plant dynamics.  Later, we will address the
issue of variable quantization, as introduced by the ADC/DAC conversion
blocks (Fig.~\ref{fig:digitalsystem}).

@@

We illustrate our approach with an example,
extracted from the literature~\cite{Franklin15}.
%
We start with a candidate solution with all coefficients zero, $K=[0
  \ 0 \ 0]^T$, and a precision of $I_p=13$, $F_p=3$.  In the first
{\sc verify} stage, the {\sc safety} check finds the counterexample
%
$ x_0 = [-0.5 \ 0.5 \ 0.5] $.
%
After adding the new counterexample to its sets of {\sc inputs}, {\sc
  synthesize} finds the candidate solution $K=[0\,0
  \,0.00048828125]^T$, which prompts the {\sc safety} verifier to
return $x_0=[-0.5\,-0.5\,-0.5]$ as the new counterexample.
